\begin{thebibliography}{1}

    % \bibitem{EPFL}
    % Shreeja Das, Santanu Mahapatra, Jehan Taraporewalla and Dipankar Saha, \say{Machine learning assisted search of thermoelectic materials with enhanced power factor, figure of merit, and air stability,} \emph{Workshop on Spintronics and Magnetism on 2D Materials, EPFL, (2021)}.
    
    % \bibitem{NMAT_Jeffrey}
    % Snyder, G., Toberer, E. \say{Complex thermoelectric materials}, \emph{Nature Mater 7, 105–114 (2008)}.
    
    % %Application
    % \bibitem{11}
    % LTspice simuator, Analog devices, available at  See \url{https://www.analog.com/en/design-center/design-tools-and-calculators/ltspice-simulator.html}
    
    
    % \bibitem{29}
    % Wang, A. P. Chandrakasan and S. V. Kosonocky,  \textquotedblleft Optimal supply and threshold scaling for subthreshold CMOS circuits, \textquotedblright Proceedings IEEE Computer Society Annual Symposium on VLSI. New Paradigms for VLSI Systems Design. ISVLSI 2002, 2002, pp. 7-11, doi: 10.1109/ISVLSI.2002.1016866.                                                                 
    
    % @article{amazon2006amazon,
    %   title={Amazon},
    %   author={Amazon, EC},
    %   journal={See https://aws. amazon. com/ec2/(15 June 2018)},
    %   year={2006}
    % }
    % Amazon, E.C., 2006. Amazon. See https://aws. amazon. com/ec2/(15 June 2018).\\

    \bibitem{company}
    Company Site, [Online]. Available: \url{https://cdrsoftwares.com/}. Accessed on: April 10, 2024.

    \bibitem{CallOneApp}
    Call One App Site, [Online]. Available: \url{https://callones.com/}. Accessed on: April 10, 2024.
    
    \bibitem{VSCode}
    VS Code, [Online]. Available: \url{https://code.visualstudio.com/}. Accessed on: April 10, 2024.

    \bibitem{RN}
    React Native, [Online]. Available: \url{https://reactnative.dev/}. Accessed on: April 10, 2024.

    \bibitem{RNF}
    React Native Firebase, [Online]. Available: \url{https://rnfirebase.io/}. Accessed on: April 10, 2024.

    \bibitem{RDT}
    RN Developer Tools, [Online]. Available: \url{https://reactnative.dev/docs/react-devtools}. Accessed on: April 10, 2024.

    \bibitem{kt}
    Kotlin, [Online]. Available: \url{https://kotlinlang.org/}. Accessed on: April 10, 2024.

    \bibitem{AB}
    Android Broadcasts overview, [Online]. Available: \url{https://developer.android.com/develop/background-work/background-tasks/broadcasts}. Accessed on: April 10, 2024.

    \bibitem{psql}
    postgreSQL, [Online]. Available: \url{https://www.postgresql.org/}. Accessed on: April 10, 2024.

    \bibitem{FLP}
    Flipper, [Online]. Available: \url{https://fbflipper.com/}. Accessed on: April 10, 2024.

    \bibitem{JWT}
    JSON Web Token, [Online]. Available: \url{https://jwt.io/}. Accessed on: April 10, 2024.

    \bibitem{NPM}
    NPM Documentation, [Online]. Available: \url{https://docs.npmjs.com/}. Accessed on: April 10, 2024.

    \bibitem{Yarn}
    Yarn Documentation, [Online]. Available: \url{https://yarnpkg.com/}. Accessed on: April 10, 2024.

    \bibitem{Nodemod}
    Node Modules Documentation, [Online]. Available: \url{https://nodejs.org/api/modules.html}. Accessed on: April 10, 2024.

    \bibitem{HTML}
    HTML, [Online]. Available: \url{https://www.w3schools.com/html/}. Accessed on: April 10, 2024.

    \bibitem{CSS}
    CSS, [Online]. Available: \url{https://www.w3schools.com/css/default.asp}. Accessed on: April 10, 2024.

    \bibitem{JS}
    JavaScript, [Online]. Available: \url{https://www.w3schools.com/js/default.asp}. Accessed on: April 10, 2024.

    \bibitem{Express}
    ExpressJS, [Online]. Available: \url{https://expressjs.com/}. Accessed on: April 10, 2024.

    \bibitem{Node}
    NodeJS Documentation, [Online]. Available: \url{https://nodejs.org/en/docs}. Accessed on: April 10, 2024.

    \bibitem{ReactJS}
    ReactJS Documentation, [Online]. Available: \url{https://react.dev/learn}. Accessed on: April 10, 2024.

    \bibitem{NodeFetch}
    Node Fetch, [Online]. Available: \url{https://www.npmjs.com/package/node-fetch}. Accessed on: April 10, 2024.

    \bibitem{Nginx}
    Nginx, [Online]. Available: \url{https://www.nginx.com/}. Accessed on: April 10, 2024.

    \bibitem{TypeScript}
    TypeScript, [Online]. Available: \url{https://www.typescriptlang.org/}. Accessed on: April 10, 2024.

    \bibitem{NextJS}
    Next.JS, [Online]. Available: \url{https://nextjs.org/}. Accessed on: April 10, 2024.

    \bibitem{Httpie}
    Httpie, [Online]. Available: \url{https://httpie.io/}. Accessed on: April 10, 2024.

    \bibitem{Puppeteer}
    Puppeteer, [Online]. Available: \url{https://pptr.dev/}. Accessed on: April 10, 2024.

    \bibitem{Baileys}
    Baileys, [Online]. Available: \url{https://whiskeysockets.github.io/}. Accessed on: April 10, 2024.

    \bibitem{LeakOSINT}
    Leak OSINT, [Online]. Available: \url{https://leakosint.com/en}. Accessed on: April 10, 2024.

    \bibitem{PDFKit}
    PDF Kit, [Online]. Available: \url{https://pdfkit.org/}. Accessed on: April 10, 2024.

    \bibitem{Git}
    Git, [Online]. Available: \url{https://git-scm.com/}. Accessed on: April 10, 2024.
    
    \bibitem{GitHub}
    GitHub, [Online]. Available: \url{https://docs.github.com/en}. Accessed on: April 10, 2024.
    
    \bibitem{Android Studio}
    Android Studio, [Online]. Available: \url{https://developer.android.com/studio}. Accessed on: April 10, 2024.
    
    \bibitem{Chromium}
    Chromium Browser, [Online]. Available: \url{https://www.chromium.org/}. Accessed on: April 10, 2024.
    
    \bibitem{DBeaver}
    DBeaver, [Online]. Available: \url{https://dbeaver.io/}. Accessed on: April 10, 2024.
    
    \bibitem{Crypto-js}
    Crypto-js, [Online]. Available: \url{https://cryptojs.gitbook.io/docs/}. Accessed on: April 10, 2024.
    
\end{thebibliography}