\thispagestyle{plain}
\begin{center}
    \Large \textbf{\uppercase{Abstract}}
\end{center}

\vspace{3\baselineskip}

\vspace{1ex}


\justify

The aim of the \textbf{Open-source Intelligence Data Mining Application}  is to assist law enforcement agencies, such as police departments, in crime investigations by generating a report based on call data records (CDRs) and tower dump data. The software is designed to provide a rapid and efficient report, enabling investigators to identify suspects.

\justify
The primary objective of this software is to provide various information about individuals, including vehicle details, location data, IMEI numbers, phone numbers, PAN numbers, MNP details, IP information, etc. The software generates a PDF report containing all relevant information about the person.
\justify
The software is designed to be scalable, allowing for future enhancements and additions to accommodate evolving data collection requirements. Its success is dependent on technical infrastructure, legal compliance, user adoption, interoperability, and training and support for successful implementation.
\justify
The software is exclusively used by police department and authorized users for crime investigation purposes. It is designed to be secure and reliable, with data validation and verification processes to ensure the accuracy and reliability of collected information. The software serves as a valuable tool for law enforcement agencies, providing them with the necessary information to conduct successful criminal investigations.
\justify
The proposed software is already in use by several law enforcement agencies, This software has some pending features under development. It is continuously updated to meet the evolving needs of law enforcement agencies and to enhance its functionality and usefulness.