
\chapter{Proposed System}\label{ch:proposed-system}
\justify

This chapter provides a detailed overview of the \textbf{{\myprojectname}}.
The project main aim is to collect Open Source and Internet Exposed information for law enforcement purposes, along with the objectives, assumptions, dependencies, and system requirements essential for its implementation.

\section{Objectives}\label{sec:objectives}

The primary objective of this application is to provide law enforcement agencies with a rapid and efficient means of analyzing call data records (CDRs) and tower dump data. C-Trace OSINT software acts as a force multiplier, empowering investigators to make informed decisions and progress their investigations more effectively. Specifically, the objectives are as follows:

\begin{enumerate}[label=\roman*.]
    \item To collect various types of information from individuals, including:
    \begin{itemize}
        \item Vehicle details
        \item Location data
        \item IMEI numbers
        \item Phone numbers
        \item PAN numbers
        \item MNP details
        \item IP information
        \item Court cases
        \item PNR information and more
    \end{itemize}
    \item To develop a caller ID app named Call One that provide default call app feature, spam call detection, collects users contacts, call logs, emails, and location information.

    \item To store the collected data securely in a PostgreSQL database for law enforcement agencies to access.

\end{enumerate}

\section{Assumptions}\label{sec:assumptions}
The successful implementation of the \textbf{{\myprojectname}} is based on the following assumptions:
\begin{enumerate}[label=\roman*.]
    \item \textbf{Availability of Necessary APIs}: The app assumes access to APIs or scraping techniques to collect data from various sources.
    \item \textbf{User Consent}: Users are assumed to provide consent for the collection of their data as per legal and ethical standards, with provisions for law enforcement access.
    \item \textbf{Data Security Measures}: Adequate security measures will be implemented to protect the collected data, especially sensitive information, from unauthorized access or breaches.
    \item \textbf{Continuous Monitoring}: Implementing continuous monitoring mechanisms to detect and respond to any unauthorized access attempts or security breaches promptly.
\end{enumerate}

\section{Dependencies}\label{sec:dependencies}
The proposed system is dependent on the following factors for its successful implementation:
\begin{enumerate}[label=\roman*.]
    \item \textbf{Technical Infrastructure}: Availability of necessary hardware, software, and network infrastructure to support app functionality.
    \item \textbf{Legal Compliance}: Adherence to legal regulations and privacy policies governing data collection and usage, including provisions for law enforcement access.
    \item \textbf{User Adoption}: User acceptance and adoption of the Call One app, with awareness of its law enforcement data collection purpose.
\end{enumerate}

\section{Requirements}\label{sec:requirements}

The requirements for implementing the {\myprojectname} include:

\subsection{Software Requirements}\label{subsec:software-requirements}

\begin{enumerate}[label=\roman*.]
    \item \textbf{.Net Framework}:  .NET Framework on Windows, Generally need a compatible Windows OS (like Windows 7, 8, 8.1, or 10) and the specific version of .NET Framework required by the app installed on system.
    \item \textbf{Chromium Browser}:  Chromium Browser is used to scrap data from websites using Puppeteer.
    \item \textbf{Node.js}: A compatible node.js version 18 or above is required to installed on the system.
    \item \textbf{Kotlin}: kotlin is need to be installed on the system to design android app.
    \item \textbf{Data Collection Modules}: Modules for collecting contacts, call logs, emails, and location information.
    \item \textbf{Database Management System}: A robust database management system for secure data storage and retrieval.
    PostgreSQL is used to store user information on database.
    \item \textbf{Security Features}: Encryption mechanisms, access controls, and authentication protocols to ensure data security.
    used AES encryption technique to encrypt the information.
\end{enumerate}

\subsection{Hardware Requirements}\label{subsec:hardware-requirements}

\begin{enumerate}[label=\roman*.]
    \item \textbf{Compatible System}: Windows Machine (like Windows 7, 8, 8.1, or 10) and the specific version of .NET Framework required by the app installed on system. 
    \item \textbf{Linux Machine}: AWS Ubuntu Linux Machine is used to run backend on it.
    \item \textbf{Compatible Devices}: The Call One app should be compatible with a range of devices, including smartphones and tablets.
\end{enumerate}