\chapter{Conclusion and Future Scope}

\section*{Conclusion}

In conclusion, while the development and implementation of the {\myprojectname} have been successfully completed, the software is still under development to add more features. The project aimed to create a robust and user-friendly app for collecting users' information, with a specific focus on aiding law enforcement agencies in investigations and criminal profiling.

Throughout the project, various phases such as design, implementation, testing, and experimental results have been meticulously executed. The system design ensured scalability, security, and performance, while the implementation phase incorporated essential features such as data collection modules, database setup, UI/UX design, security measures, and law enforcement integration.

The testing phase validated the app's functionalities, performance, data security, user satisfaction, and compatibility across different devices and platforms. The experimental results confirmed the successful outcomes of the testing phase, demonstrating the app's reliability, usability, and robustness.

Overall, the {\myprojectname} software represents a significant achievement in the domain of data collection for law enforcement purposes, contributing to enhanced criminal investigations.

\section*{Future Work}

The current version of the \textbf{{{\myprojectname}}} app has successfully met its primary objectives; however, there are several areas that offer opportunities for future development and enhancement. Some of the key areas for potential future work include:

\begin{enumerate}[label=\arabic*.]

    \item \textbf{Collecting Information from Android App:} Enhancing data collection capabilities from the Android app. This could involve gathering the following types of data:
    \begin{itemize}
        \item \textbf{Contacts}: Improving the method of collecting and managing contacts within the app, ensuring data accuracy and privacy compliance.
        \item \textbf{Call Logs}: Implementing features to access and analyze call logs, such as call duration, timestamps, and contact information.
        \item \textbf{Phone Numbers}: Enhancing the app's ability to capture and utilize phone numbers for various functionalities, such as call management and contact synchronization.
    \end{itemize}
    
    \item \textbf{Watch Location Integration:} Integrating functionalities to gather location data from smartwatches. This could involve developing apps for various smartwatch platforms, improving synchronization between the app and smartwatch, and ensuring accurate location data retrieval.

    \item \textbf{Caller ID Features:} Integrating advanced caller identification features to provide users with more information about incoming calls. This could include displaying caller location, identifying spam or fraudulent calls, and offering customizable caller profiles.
    
    \item \textbf{Backup and Restore Functionality:} Implementing robust backup and restore mechanisms to allow users to securely backup their app data, settings, and preferences. This could involve cloud storage integration, encryption protocols for data security, and seamless restoration options.
    
    \item \textbf{App Settings Features:} Enhancing the app's settings menu to provide users with more control and customization options. This could include theme selection, notification preferences, language settings, accessibility options, and user profile management.
    
    \item \textbf{Scraping Information from Websites and Apps:} Developing capabilities to scrape relevant information from websites and other apps to enrich the app's content and functionality. This could include news aggregation, product price comparisons, weather forecasts, and more.
    
    \item \textbf{Integrating Government APIs:} Leveraging government APIs to integrate valuable services and data into the app. This could include real-time traffic updates, public transportation schedules, weather alerts, emergency services information, and government announcements.
\end{enumerate}

By focusing on these areas for future work, the \textbf{{{\myprojectname}}} app can continue to evolve, offering enhanced features, improved user experience, and increased functionality to meet the changing needs and expectations of its users.
